01 - Simulate data

### 2023-12-02 scripts/01_sim_data.qmd
add analyses

```{r}
#| label: setup

@@

dat1 <- tibble(
  score = unlist(score_subjs),
  proficiency = unlist(proficiency_subjs),
  subj = as.factor(paste("s", rep(1:subjs, each = timep), sep = "")),
  time = rep(0:10, length.out = subjs * timep)
)
```

@@

## Data 2:

We simulate word-final vowel reduction in learners of Spanish.

@@

```{r}
set.seed(my_seed)

subjs <- 60
timep <- 9
reps <- 6

@@

  # Add eud to dat2
  this_row$eud <- list(this_eud)
  this_trial <- unnest(this_row, eud)
  this_trial$timep <- 1:timep
  dat2 <- bind_rows(dat2, this_trial)
}

dat2 <- dat2 %>%
  mutate(
    id = paste(group, subj, rep, sep = ".")
  )
```

```{r}
dat2 %>%
  ggplot(aes(timep, eud, group = id, colour = group)) +
  geom_path(alpha = 0.15, linewidth = 1) +
  facet_grid(cols = vars(vowel), rows = vars(group))
```

```{r}
dat2 %>%
  ggplot(aes(timep, eud, colour = group)) +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 3)) +
  facet_grid(cols = vars(vowel), rows = vars(group))
```

```{r}
dat2 %>%
  filter(subj == 1, group == "es_0") %>%
  ggplot(aes(timep, eud, group = id, colour = as.factor(rep))) +
  geom_path() +
  facet_grid(cols = vars(vowel))
```

>>>>

```{r}
#| label: setup
#| message: false

@@

dat1 <- tibble(
  score = unlist(score_subjs),
  proficiency = unlist(proficiency_subjs),
  subj = as.factor(paste("s", rep(1:subjs, each = timep), sep = "")),
  time = rep(0:10, length.out = subjs * timep)
)

saveRDS(dat1, "data/dat1.rds")
```

@@

## Data 2: Time-series

We simulate word-final vowel reduction in learners of Spanish (simultaneous bilinguals, beginner late bilinguals and advanced late bilinguals).

@@

```{r}
#| label: dat2

subjs <- 20
timep <- 9
reps <- 6

@@

  # Add noise
  this_eud <- this_eud + rnorm(9, 0, 0.05)
  # Add eud to dat2
  this_row$eud <- list(this_eud)
  this_trial <- unnest(this_row, eud)
  this_trial$timep <- 1:timep
  dat2 <- bind_rows(dat2, this_trial)
}

dat2 <- dat2 %>%
  mutate(
    id = paste(group, subj, rep, sep = ".")
  )

saveRDS(dat2, "data/dat2.rds")
```

```{r}
#| label: dat2-plot

dat2 %>%
  ggplot(aes(timep, eud, group = id, colour = group)) +
  geom_path(alpha = 0.15, linewidth = 1) +
  facet_grid(cols = vars(vowel), rows = vars(group))
```

```{r}
#| label: dat2-template

dat2 %>%
  ggplot(aes(timep, eud, colour = group)) +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 3)) +
  facet_grid(cols = vars(vowel), rows = vars(group))
```

```{r}
#| label: dat2-subj-1

dat2 %>%
  filter(subj == 1, group == "es_0") %>%
  ggplot(aes(timep, eud, group = id, colour = as.factor(rep))) +
  geom_path() +
  facet_grid(cols = vars(vowel))
```

```{r}
#| label: dat2-gam

dat2_gam <- gam(eud ~ s(timep, by = interaction(vowel, group), k = 9), data = dat2)
summary(dat2_gam)
```
